Learning words through recursive pragmatic reasoning about other agents

### 2013-05-30 praglearn.tex
figure updates

@@

@@

@@

@@

\subsubsection{Lexicaliation and preservation of scalar implicature}

>>>>

% Simulation parameters:
%   prior on meaning of "some": dirichlet(10, 10)
%   prior on meaning of "all": dirichlet(1, 10)
%
% How speaker refers to "some" and "all" objects:
% array([[  9.99951162e-01,   2.87541198e-03],
%        [  4.88378335e-05,   9.97124588e-01]])
%
% How listener interprets "some" and "all" words:
% array([[ 0.86214895,  0.13785105],
%        [ 0.03151434,  0.96848566]])

@@

% Simulation parameters:
%   word costs: 0.5, 1.0
%   object prior: 0.8, 0.2
%
% How speaker refers to "common" and "rare" objects:
% array([[ 0.88491473,  0.53858973],
%        [ 0.11508527,  0.46141027]])
%
% How listener interprets "cheap" and "expensive" words:
% array([[ 0.77458316,  0.22541684],
%        [ 0.64702551,  0.35297449]])

@@

\begin{figure}
  \centering
  \includegraphics[width=0.20\textwidth]{figures/cross-sit.pdf}
  \caption{Cross-situational simulation}
  \label{fig:cross-sit}
\end{figure}

@@

% Novel word means: Familiar object: 25.5%. Novel object: 74.5%.
% To anti-sparse listener, novel word means: Familiar object: 21.4%. Novel object: 78.6%.
% To sparse listener, novel word means: Familiar object: 30.5%. Novel object: 69.5%.

\begin{figure}
  \centering
  \includegraphics[width=0.20\textwidth]{figures/ME-1dax.pdf}
  \includegraphics[width=0.20\textwidth]{figures/ME-flat-10dog-10dax.pdf}
  \includegraphics[width=0.20\textwidth]{figures/ME-antisparse-10dog-10dax.pdf}
  \includegraphics[width=0.20\textwidth]{figures/ME-sparse-10dog-10dax.pdf}
  \caption{Mutual exclusivity simulation}
  \label{fig:mutual-exclusivity}
\end{figure}

@@

% To show that they're lexicalized, at end of each of 4 dialogues, we
% look at how speaker and listener talk about/interpret the objects/words:
%
% Dialogue 0, after disabling implicature:
%   How speaker refers to "common" and "rare" objects:
% array([[  9.99994601e-01,   1.67862018e-02],
%        [  5.39888463e-06,   9.83213798e-01]])
%   Listener's interpretation of "cheap" and "expensive" words:
% array([[ 0.84765063,  0.15234937],
%        [ 0.02451694,  0.97548306]])

% Dialogue 1, after disabling implicature:
%   How speaker refers to "common" and "rare" objects:
% array([[  9.99997339e-01,   1.04639034e-02],
%        [  2.66058112e-06,   9.89536097e-01]])
%   Listener's interpretation of "cheap" and "expensive" words:
% array([[ 0.86951534,  0.13048466],
%        [ 0.01986478,  0.98013522]])

% Dialogue 2, after disabling implicature:
%   How speaker refers to "common" and "rare" objects:
% array([[  9.99984637e-01,   2.19135388e-02],
%        [  1.53629560e-05,   9.78086461e-01]])
%   Listener's interpretation of "cheap" and "expensive" words:
% array([[ 0.83486332,  0.16513668],
%        [ 0.03421814,  0.96578186]])

% Dialogue 3, after disabling implicature:
%   How speaker refers to "common" and "rare" objects:
% array([[  9.99996148e-01,   1.92821280e-02],
%        [  3.85172462e-06,   9.80717872e-01]])
%   Listener's interpretation of "cheap" and "expensive" words:
% array([[ 0.83985034,  0.16014966],
%        [ 0.02170542,  0.97829458]])

\subsubsection{Lexicalization and preservation of scalar implicature}
